---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%"
)
```

# SETr

<!-- badges: start -->
<!-- badges: end -->

The goal of SETr is to simplify calculations and make graphs for QA/QC and communication of Surface Elevation Table (SET) data.  

This package is based on functions created as part of a larger workflow. All code for that project is also on [GitHub, here](https://github.com/swmpkim/SETr_Reserve_Template); and at the top of the README for that repo are links to publicly available project outputs. Most of the functions here were used in the [Reserve-level technical reports](https://drive.google.com/drive/folders/1ExY94WWOoS3iY3iJpKdteI96_iFnDdMM?usp=sharing). Please see the package vignette for details on using this package. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("swmpkim/SETr")
```
## Example

This is a basic example which shows you how to make a simple graph of change since the first reading at each SET:

```{r example, message = FALSE, warning = FALSE}
library(SETr)

# first, perform cumulative change calculations
cumu_set <- calc_change_cumu(example_sets)

# now plot cumulative change by SET
plot_cumu_set(cumu_set$set)

# or by arm, at a single SET
plot_cumu_arm(cumu_set$arm)
```
